CF Registry Analysis

### 2023-12-01 Christine Chan/CF Registry/cf_registry_analysis.qmd
parallel registry (needs more RAM)

```{r}
#| include: false
library(Hmisc)
library(tidyverse)
library(forestmodel)
library(childsds)
library(gt)
library(gtsummary)
library(forcats)
library(labelled)
```

@@

```{r results='asis',fig.height=10,fig.width=10}
invisible(lapply(unique(annual$ReviewYear), function(y) {
  cat("\n")
  cat("### ", y)
  cat("\n")
  log_reg(y)
  cat("\n")
}))
```

>>>>

```{r}
#| include: false
library(Hmisc)
library(tidyverse)
library(forestmodel)
library(childsds)
library(gt)
library(gtsummary)
library(forcats)
library(labelled)
library(parallel)
```

@@

```{r results='asis',fig.height=10,fig.width=10}
cl = makeCluster(16,type = "FORK")
invisible(parLapply(cl,unique(annual$ReviewYear), function(y) {
  cat("\n")
  cat("### ", y)
  cat("\n")
  log_reg(y)
  cat("\n")
}))
stopCluster(cl)
```
